---
title: "Introduction to SAST"
output: rmarkdown::html_document
vignette: >
  %\VignetteIndexEntry{Introduction to SAST}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
<style type="text/css">
.main-container {
  max-width: 1200px;
  margin-left: auto;
  margin-right: auto;
}
</style>
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.height=3,
  fig.width=12
)
```

# 1. Package Loading
Here we load the essential packages for running this vignette. Specifically:

* **SAST**: our main R package which contains the data-driven SAST procedure for online FDR control.
* **tidyverse**: data-wrangling function used for processing.
* **kedd**: used for cross-validated bandwidth determination.
* **np**: for estimating conditional densities.
* **onlineFDR**: onlineFDR R package, which includes multiple p-value based online FDR procedures, e.g. LORD, LOND, ADDIS, etc.
* **pbmcapply, parallel**: parallel computing package.
```{r setup, results='hide'}
library(SAST)
library(tidyverse)
library(kedd)
library(np)
library(pbmcapply)
library(onlineFDR)
library(parallel)
library(grid)
library(gridExtra)
library(reshape2)
library(snow)
library(jcolors)
```

# 2. Simulation
In this section, we consider a basic simulation setting to demonstrate the usage of SAST. We also compare SAST with other online FDR methods, speicifically using the R package **onlineFDR**.

## 2.1 Simulation Setting (constant signal proportion)
We let $m=5000$, signal strength $\mu=2.6,2.8,3$ (small signal strength to demonstrate the power of our procedure), signal variance $\sigma^2=1$, constant $\pi_s=0.05$, number of iteration $200$, initial burn-in period to be $init=500$. FDR levels are evaluted from location 200 to 5000 with step-size 400. 

Then we let the covariate bandwidth $h$ to be chosen by the **h.ccv** function, here it's $38.37824$.
```{r simulation-setting}
m <- 5000
mu <- c(2.6,2.8,3)
nCores <- detectCores()
p <- rep(0.05,m)
alpha <- 0.05
nrep <- 200
init <- 500
t <- seq(200,m,400)
grid <- expand.grid(mu,1:nrep)
#h <- h.ccv(1:m)
h <- 38.37824
```

## 2.2 Running Simulation
We first write a small worker function that runs SAST, LOND, LORD++, and ASDDIS:
```{r running-simulation, results='hide'}
workerFunc <- function(m,mu,sigma=1,p,iter,alpha=0.05,init,t,h){
  #Generate data
  x.Obs <- x.Real <- rep(0,m)
  #Ground Truths, p here is a vector of proportions
  x.Real <- p %>% map_dbl(~sample(c(0,1),1,prob=c(1-.x,.x)))
  theta <- x.Real*mu
  #Observations for x
  x.Obs <- theta %>% map_dbl(~rnorm(1,.x,sigma))
  zval <- x.Obs/sigma
  pval <- 2*pnorm(-abs(zval))
  
  res_SAST.raw <- SAST(zval,alpha,init,h=h,conservative=FALSE)
  res_lond.raw <- LOND(pval,alpha)
  res_lord_plus.raw <- LORD(pval,alpha)
  res_addis.raw <- ADDIS(pval,alpha)
  
  res_lond <- t %>% map(~FDP_MDP(x.Real,res_lond.raw$R,.x)) %>% unlist %>% split(.,names(.))
  res_lord_plus <- t %>% map(~FDP_MDP(x.Real,res_lord_plus.raw$R,.x)) %>% unlist %>% split(.,names(.))
  res_addis <- t %>% map(~FDP_MDP(x.Real,res_addis.raw$R,.x)) %>% unlist %>% split(.,names(.))
  res_SAST <- t %>% map(~FDP_MDP(x.Real,res_SAST.raw$decision,.x)) %>% unlist %>% split(.,names(.))
  
    return(list(mu=mu,iter=iter,t=t,
              lond_FDP=res_lond$FDP,
              lond_MDP=res_lond$MDP,
              lord_plus_FDP=res_lord_plus$FDP,
              lord_plus_MDP=res_lord_plus$MDP,
              addis_FDP=res_addis$FDP,
              addis_MDP=res_addis$MDP,
              SAST_FDP=res_SAST$FDP,
              SAST_MDP=res_SAST$MDP))
}

#function to generate legend for plot
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

# calculate FDP and MDP given the decision and the truth for data until time t
FDP_MDP <- function(x.Real,dec,t){
  if (sum(dec[1:t])!=0){
    FDP <- sum((1-x.Real[1:t])*dec[1:t])/(sum(dec[1:t]))
  } else {
    FDP <- 0
  }
  if (sum(x.Real[1:t])!=0){
    MDP <- sum(x.Real[1:t]*(1-dec[1:t]))/sum(x.Real[1:t])
  } else {
    MDP <- 0
  }
  return(list(FDP=FDP,MDP=MDP,t=t))
}

#res<-pbmcmapply(workerFunc,mu=grid[,1],iter=grid[,2],MoreArgs=list(m=m,p=p,init=init,t=t,h=h),mc.cores=1)
cl <- makeCluster(nCores)
clusterCall(cl,function(){
library(SAST)
library(tidyverse)
library(kedd)
library(np)
library(pbmcapply)
library(onlineFDR)
library(parallel)
library(grid)
library(gridExtra)
library(reshape2)
library(snow)
library(jcolors)
})
clusterCall(cl,assign,'FDP_MDP',FDP_MDP,envir=.GlobalEnv)
res<-clusterMap(cl,workerFunc,mu=grid[,1],iter=grid[,2],MoreArgs=list(m=m,p=p,init=init,t=t,h=h))
stopCluster(cl)
```

## 2.3 Results
```{r plot}
#cleaned_res<-as_tibble(t(res)) %>% unnest(mu,iter) %>% unnest()
cleaned_res <-res %>% map_df(as_tibble)
mean_res<-cleaned_res  %>%  group_by(mu,t) %>% dplyr::select(-c('iter')) %>% summarise_all(list(mean)) %>% group_by(mu,t)
FDR_res <- dplyr::select(mean_res,contains("FDP"));
MDR_res <- dplyr::select(mean_res,contains("MDP"));
colnames(MDR_res) <- colnames(FDR_res) <- c('mu','t','LOND','LORD++','ADDIS','SAST')

#Plotting FDR and MDR respectively
res_FDR_long <- melt(FDR_res,id=c("mu","t"));
res_MDR_long <- melt(MDR_res,id=c("mu","t"));

p_FDR <- ggplot(data=res_FDR_long,aes(x=t,y=value,colour=factor(variable),shape=factor(variable)))+
  geom_point(size=2.5)+
  geom_line(size=1)+
  facet_wrap(~mu,ncol=3,labeller=label_both)+
  ylim(0,0.12)+
  xlab(expression(t))+ylab("FDR")+
  theme(legend.position="bottom")+
  ggtitle("Intermediate FDR level Comparison")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
    panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  theme(plot.title=element_text(hjust=0.5))+scale_color_jcolors(palette = "pal3")+
  labs(color  = "Methods", linetype = "Methods", shape = "Methods")


p_MDR <- ggplot(data=res_MDR_long,aes(x=t,y=value,colour=factor(variable),shape=factor(variable)))+
  geom_point(size=2.5)+
  geom_line(size=1)+
  facet_wrap(~mu,ncol=3,labeller=label_both)+
  ylim(0.5,1)+
  xlab(expression(t))+ylab("MDR")+
  theme(legend.position="none")+
  ggtitle("Intermediate MDR level Comparison")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
    panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  theme(plot.title=element_text(hjust=0.5))+scale_color_jcolors(palette = "pal3")

mylegend <- g_legend(p_FDR);
grid.arrange(arrangeGrob(p_FDR + theme(legend.position="none"),
                         p_MDR + theme(legend.position="none"),
                         ncol=2),
             mylegend, nrow=2,heights=c(10, 1), top = "Methods Comparison (constant p 0.05)")
```




